%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Passion Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {https://github.com/nchalkley2/ImgboardServer} % Job title
	{Microservice Image Board Server} % Organization
    {} % Location
    {July 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created in C++/Python using IncludeOS.}
		\item {Utilizes a microservice architecture to do webserver hosting in parallel.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {https://github.com/nchalkley2/LandscapeGenerator} % Job title
	{GPU-Accelerated Landscape Generator} % Organization
    {} % Location
    {December 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Inspired by Bob Ross, the video game Dwarf Fortresses' world generation, and the CPU-only landscape generation program World Machine.}
		\item {Uses Unreal Engine 4's blueprint system for non-destructive node based generation.}
		\item {Uses GPU processing to generate landscapes with simulated erosion.}
		%\item {Currently in progress. I hope to finish this project and publish it before summer 2018.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {https://github.com/nchalkley2/UE4-SS13} % Job title
	{Unreal Engine 4 Space Station Simulation Game} % Organization
    {} % Location
    {Spring 2014 - Winter 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	  	\item {Created a multiplayer space station simulation game based on the game Space Station 13.}
		\item {Used the game engine Unreal Engine 4.}
		\item {Integrated the OpenCL and OTL libraries with Unreal Engine for the project. Used OpenCL for the atmospheric simulation and MySQL with the OTL library for storing player data and committing database transactions.}
		\item {Used Marvelous Designer for the player clothes.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
