%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Gameplay Programmer} % Job title
	{EQ-Games} % Organization
    {Atlanta, GA} % Location
	{February 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	  	\item {Currently developing unannounced multiplayer mech fighting game in Unreal Engine 4.}
        \item {Writing C++ gameplay programming for the aforementioned project.}
        \item {Writing the networking code for the multiplayer features in the aforementioned project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Artist} % Job title
	{Beam Imagination} % Organization
    {Atlanta, GA} % Location
	{January 2018 - December 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	  	\item {Created AR/VR apps for the Atlanta Braves with Beam using photogrammetry.}
        \item {Coordinated and directed photogrammetry of individual Braves players.}
        \item {Designed/modeled a realtime 3d demonstration of a prototype Delta Air Lines in-flight beverage cart.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Environment Artist} % Job title
	{Student Innovation Fellowship (SIF)} % Organization
    {Georgia State University} % Location
    {Summer 2016 - January 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modeled buildings for the SIF 3d Atlanta Project. The project is a historical recreation of Atlanta in the early 20th century.}
        \item {Conducted photogrammetry for the SIF Oakland Cemetery 3d archival project and the Kell Hall archival project.}
        \item {Assisted Georgia State University course designers on integrating 3d modeling classes into SIF projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Makerspace Assistant} % Job title
%	{EXLAB/Makerspace} % Organization
%    {Georgia State University} % Location
%    {Winter 2015 - Summer 2016} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Wrote documentation/tutorials on how to use the EXLAB equipment.}
%        \item {Backend/frontend website development for the EXLAB wiki.}
%        \item {Designed 3d printed models.}
%        \item {Developed showcase projects for emergent technologies such as the Oculus Rift and the Microsoft Hololens.}
%      \end{cvitems}
%    }

\end{cventries}

